At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families - Supporting Information

### 2019-11-28 manuscript/reply_to_referees_2.tex

		\begin{refquote}
			L322 – how was this result obtained if insect phylogenies were not calculated? Do you mean “more closely-related plants in pollinator networks”?
		\end{refquote}

@@

			\smallskip

			p. 5, l. 69-71 « In either case, dissimilarity (…). » This sentence helped me to understand why it is important to look at unshared interactions. To be better showcased ?

		\end{refquote}

		\textbf{R:} The number of shared and unshared interactions are both dependent variables included in the analysis. The number of shared variables is indeed the key variable, but the number of unshared interactions is also important as it indicates how extraordinary a particular number of shared interactions is. The binomial process incorporates both quantities; converting the numbers of shared and unshared interactions to a proportion and weighting the observations by the total number of interactions. We thank the Referee for pointing out text in the introduction which clarified the purpose of including unshared interactions. We have expanded the beginning of this section to explain the logic of our modelling approach in more detail.

		lines 130-141:

@@

		\begin{quotation}

			We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared and unshared interaction partners ($M_{ij}$, $U_{ij}$, respectively). 
			The number of unshared interaction 
			partners gives valuable information about cases where, for example, 
			closely-related plants may have experienced disruptive selection, leading to weaker phylogenetic signal. 
			The sum $M_{ij} + U_{ij}$ indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of extreme specialists with one common interaction partner.

			Together, $M_{ij}$ and $U_{ij}$ give a Jaccard index ($J_{ij}$) describing 
			the proportion of shared interactions. $J_{ij}$ is defined: 
			\begin{equation}
			J_{ij} = \frac{M_{ij}}{U_{ij}+M_{ij}} ,
			\end{equation}
			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$.

@@

		\textbf{R:} Yes, this analysis is also using a Jaccard index, but we see how the previous version did not make this clear. We now state that both the tuple and proportional glm's use Jaccard dissimilarity. We also re-iterate the logic behind the tuple-based formulation in this paragraph.

			Lines 173-181:

			\begin{quotation}

				To demonstrate the power of defining $J_{ij}$ as a tuple of $M_{ij}$ and $U_{ij}$ rather than a single value, we repeated the above analyses using a Jaccard index based only on the proportion of interaction partners that are shared (i.e., $J_{ij}$ = $M_{ij}$/[$M_{ij}+U_{ij}$]). Note that while the proportion of shared interaction partners is the same in both cases, the tuple formulation gives more weight to plants with many interaction partners as these provide more information. When comparing the two approaches 
				we observed similar trends but, notably, the tuple definition of $J_{ij}$ had greater power to detect weak relationships (\emph{Supporting information 2}). We therefore show only the results when defining $J_{ij}$ as a tuple in the main text.

@@

	4. Permuting the permuted networks is confusing [[done]]

		\begin{refquote}
			* Evaluating type I and type II errors: Permutations of permutations
			Paragraph p. 10, l. 187-197 is a bit confusing because of phrasings such as “permutations/permuting of the permuted networks”. I don't have a better way to name this second round of permutations, but the overall is difficult to follow and could be shortened while still conveying the same message.
			Actually, I find the comment in Supplementary information 3 clearer, although no reference to Supplementary information 3 is made.
			Besides, as slopes of regressions in permuted networks are tightly grouped around zero (Fig. 2, thin lines indicating 
			extrema of slopes distribution overlapping each other), so type II errors do not seem to be a big problem here.
		\end{refquote}

		\textbf{R:} We agree with the Referee about the difficulty of describing this procedure. We have added an extra line to further explain the logic behind the second round of permutations and hope that this will clarify the goal of these analyses. We have also added a reference to Supplementary Information 3 and thank the Referee for pointing out the oversight.

		Lines 209-212:

			This permutation approach also allows us to estimate type I and type II 
			error for our analysis. Because the permuted networks should not demonstrate any particular relationship between phylogenetic distance and partner overlap, these slopes should be similar to those obtained after permuting these networks a second time.

@@

		\textbf{R:} The Referee makes a very good point. We had considered these high numbers of significant slopes unlikely to occur by chance, even if we would expect one or two significant results by chance. This argument is somewhat difficult to make convincingly and briefly in the middle of the manuscript, however. Instead, we apply the sequential correlated Bonferroni test in~\citet{Drezner2016}. This development of this test was heavily motivated by the Moran paper you recommend, and we thank the Referee for pointing out this literature. We have added tables of the SCBT critical values to Supplemental Information 4 in order to provide readers with a bit more detail. We have also added a few lines to the methods to formally introduce the problem of multiple testing, some of the objections to the strict Bonferroni in~\citet{Moran2003}, and our solution to it.

		Lines 278-285:

		\begin{quotation}

			By considering each family separately, we do risk obtaining some significant results purely by chance. The standard technique for addressing this type of multiple hypothesis testing, the Bonferroni correction, tends to be over-zealous and lead to a failure to reject the null hypothesis even when a large number of significant results before the correction supports the alternative hypothesis~\citep{Moran2003}. To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezner2016} (\emph{Supplemental Information 4}).

@@

		\end{quotation}

		Lines 355-360 now read:

		\begin{quotation}
			 In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table 1; Fig. 3). If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supplemental Information 4}).
		\end{quotation}

@@

		\textbf{R:} We share the Referee's desire to prompt researchers to share their sampling effort, and have added a short mention of the possibility  that some of our specialists are actually just rare.

		Lines 386-391:

		\begin{quotation}

			Note that some of the apparent specialists in our dataset may actually be rare species involved in more interactions which have not yet been observed~\citep{Bluthgen2006,Poisot2015}. Without information on the sampling completeness of the networks in our dataset, it is difficult to estimate the size of this effect. 
			It is possible, however, that we might observe stronger relationships between phylogenetic
			distance and niche overlap with more complete data on rare species.

@@

		\textbf{R:} We thank the Referee for their suggestions and for the small reading list. We have revised this paragraph along the lines above and hope that it is now clearer. We have expanded our discussion of (potentially) conflicting selection from different interaction types and removed our brief reference to dynamical drivers. We believe that sticking more closely to a single theme has helped to focus this paragraph. It now reads:

		\begin{quotation}

			For those few families which were well-represented in \emph{both} pollination
			and herbivory networks, we can also contrast the 
			trends in the two network types. Notably, all families except \emph{Asteraceae} 
			showed different trends in different network types. 
			This could be because of conflicting selection from pollinators and herbivores,
			with one type of selection placing greater constraints on plant traits than the other.
			Multiple types of interactions (e.g., pollination, herbivory, nectar robbing) 
			and even environmental factors can influence traits such as 
			flower colour, nectar abundance, and flowering phenology~\citep{Strauss2006}. 
			These influences can act in the same or different directions~\citep{Strauss2006}.
			Plant phenotypes in turn affect which species participate in both pollination and herbivory~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
			The interplay between these different selective pressures may mean that plants
			cannot evolve to respond optimally to both pollinators and herbivores. Put another
			way, stronger selective pressure from herbivores might cause phenotypic changes
			that disrupt phylogenetic signal in pollinators, or vice versa. This could result from
			asymmetric degree distributions: within a single system, most plants tend to interact
			with many pollinators \emph{or} many herbivores but not both~\citep{Melian2009,Pocock2012,Astegiano2017}.
			These asymmetric interactions may also affect higher-order network structures such as
			modularity or nestedness~\citep{Astegiano2017}. The nature of the effects of multiple interaction types on both phylogenetic signal in interactions and overall network structure is, however, still an open question deserving of much more research.

@@

	  	We hope that this revised version reads better.

	12. ?Suggestion to remove long list of citations in lines 22-25? [[done]]

		\begin{refquote}
			p. 3, l. 22-25 : There is a lot of citations here. I agree they all point to « mixed results » but this pertains to different aspects of phylogenetic signal. Some highlight differences between mutualistic and antagonistic systems, other rather focus on difference of phylogenetic signal between trophic levels, or even focus on subset of interaction networks. I think, it would be more relevant to the reader to cite these different works to explain how mixed results are (as done in the text following this long citation list).
		\end{refquote}

		\textbf{R:} We had intended these citations to showcase a selection of researchers addressing different aspects of phylogenetic signal, but appreciate how including them all together could be confusing. We have removed the large list so as not to distract from the more specific citations in subsequent lines.

@@

		\textbf{R:} We thank the Referee for noticing this line, and have added a bit more detail as to how this pairwise perspective allows us to consider both whole-network trends and trends within families.

		Lines 79-86:

		\begin{quotation}

			Whereas previous 
			studies have focused on the presence or absence of phylogenetic
			signal across entire networks, we take a pairwise perspective in
			order to obtain a more detailed picture of how plant phylogeny
			relates to network structure. As different plant families (which represent tractable clades for analysis) may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network. 
			This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales.

@@

		\textbf{R:} We have added the countries or regions (e.g., islands associated with mainland countries, such as Greenland and Denmark) to Table 1 in the SI. We hope that this will provide enough clarification about the spatial scale of our dataset. For readers who are interested, we now refer both to the original sources and from an online database (the Web of Life dataset) which collects the pollination networks we used. These sources can be used to obtain more exact coordinates.

	13. Suggestions to clarify explanation of regressions [[done?]]

		\begin{refquote}
			p. 7, l. 125-141 : I think the beginning of this section should be more straightforward and contrast better the information provided by M\_ij and U\_ij (starting with them) with that of the Jaccard index J\_ij. In addition, J\_ij is never mentioned again as such (but is an estimate of w\_ij).
		\end{refquote}

		\textbf{R:} We have reworded this section in an attempt to clarify the relationships between $M_{ij}$, $U_{ij}$, and $J_{ij}$ and better contrast the information given by each value. We have also changed all $\omega_{ij}$ to $J_{ij}$ for simplicity. This paragraph (lines 130-146) now reads:

			We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared and unshared interaction partners ($M_{ij}$, $U_{ij}$, respectively). 
			The number of unshared interaction 
			partners gives valuable information about cases where, for example, 
			closely-related plants may have experienced disruptive selection, leading to weaker phylogenetic signal. 
			The sum $M_{ij} + U_{ij}$ indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of extreme specialists with one common interaction partner.

			Together, $M_{ij}$ and $U_{ij}$ give a Jaccard index ($J_{ij}$) describing 
			the proportion of shared interactions. $J_{ij}$ is defined: 
			\begin{equation}
			J_{ij} = \frac{M_{ij}}{U_{ij}+M_{ij}} ,
			\end{equation}
			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$.
			In our statistical analyses (see below), we used the tuple ($M_{ij}$, $U_{ij}$) as the
			dependent variable rather than the single value $J_{ij}$. 
			This allows us to preserve information about the amount of information provided by each pair of plants and weight the observations accordingly.
			Note that species sharing a large \emph{number} of interaction partners may not share a large \emph{proportion} of interaction partners if the number of interaction partners that are not shared is also large.

@@

	15. Typo in page 15, lines 322-324 [[done]]

		\begin{refquote}
			p. 15, l. 322-324 “ More closely-related pollinators did, however, tend to share fewer interaction partners (…).”: This is the first time that conservatism of interactions is checked from the pollinators perspective in the manuscript. Is it a typo or did I miss something in the manuscript?
		\end{refquote}

		\textbf{R:} Yes, this is indeed a typo. We did not have information on pollinator phylogenies and did not test anything from the pollinator perspective. We thank the Referee for pointing this out, and have corrected the line. The sentence now reads:

		Lines 350-352:

		\begin{quotation}
			Plants in pollination networks did, however, have a lower intercept probability of sharing interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
		\end{quotation}
